\texttt{ensmallen}: a flexible C++ library for efficient function optimization

### 2018-10-18 doc/mlsys_paper/paper.tex
better flow for mentioning mlpack
remove blank space around the plot in figure 2(b)
added citations to many optimisation algorithms

% I guess to save some space we should group them.
%% CS: should we add citations to some (or all) of the listed optimisers?
%% CS: the MLSYS CFP states that "papers can be up to 6 pages (not including references)",
%% CS: so technically we can have 10000+ references.
\vspace*{-0.4em}
\begin{enumerate}[{~~~$\bullet$}]
\small
  \item {\bf SGD variants}~\cite{Robbins_1951,kingma2015adam}:
      Stochastic Gradient Descent (SGD),
      SGD with Restarts,
      Parallel SGD (Hogwild!),
      Stochastic Coordinate Descent, 
      SMORMS3, AdaGrad,
      AdaDelta, RMSProp, Adam, AdaMax

@@

  \item {\bf Genetic variants}:
        Conventional Neuro-evolution,
        Covariance Matrix Adaptation Evolution Strategy

  \item {\bf Other}: Conditional Gradient Descent, Frank-Wolfe algorithm, Simulated Annealing~\cite{kirkpatrick1983optimization}

@@

using namespace ens;
StandardSGD<>().Optimize(lrf, sgdModel);
Adam().Optimize(lrf, adamModel);
AdaGrad().Optimize(lrf, adagradModel);
SMORMS3().Optimize(lrf, smorms3Model);
SPALeRASGD().Optimize(lrf, spaleraModel);
RMSProp().Optimize(lrf, rmspropModel);
\end{minted}
\caption{Code.}
\end{subfigure}
\begin{subfigure}[b]{0.49\textwidth}
  \centering
  % \includegraphics[width=\textwidth,height=0.45\textwidth]{experiments/learning_curves_crop.png}
  \includegraphics[width=\textwidth,height=0.6\textwidth]{experiments/learning_curves_crop.eps}
\caption{Learning curves.}
\end{subfigure}
\caption{\footnotesize
Example usage of six \texttt{\small ensmallen} optimizers to optimize a
linear regression function on the \texttt{\small YearPredictionMSD}
dataset~\cite{ucimlrepository} for 5 epochs of training.  The optimizers can be
tuned for better performance.}
\label{fig:learning_curve}
\vspace*{-1ex}
\end{figure}

@@

% RC: I think it's really important to highlight ensmallen's usage (and
% genesis), although I can't find the right words to concisely and non-awkwardly
% say that we wrote ensmallen as part of mlpack originally.
\texttt{\small ensmallen} is already in use as the optimization toolkit of the
\texttt{\small mlpack} machine learning library~\cite{mlpack2018}.

We aim to expand the library with further optimization techniques
as the need arises.  Since {\tt ensmallen} is open source,
external contributions to the codebase are welcome.
For more information on the
toolkit, see the website and documentation at
\href{https://www.ensmallen.org}{\tt\small https://www.ensmallen.org}.

>>>>

%% CS: WARNING !!!!
%% CS: can't add more citations without causing the item with SGD variants
%% CS: to overflow into 3 lines.
%% CS: this causes a cascade effect of mucking up the entire layout of
%% CS: the paper, causing the main text to spill over to 7 pages.
%% 
%% CS: the citations below should be sufficient; 
%% CS: this is a workshop paper, not a journal article

\vspace*{-0.4em}
\begin{enumerate}[{~~~$\bullet$}]
\small
  \item {\bf SGD variants}~\cite{Ruder_2016}:  % Robbins_1951 is semi-related
      Stochastic Gradient Descent (SGD),
      SGD with Restarts,
      Parallel SGD (Hogwild!)~\cite{hogwild_nips_2011},
      Stochastic Coordinate Descent, 
      AdaGrad~\cite{Duchi_2011},
      AdaDelta~\cite{Zeiler_2012},
      RMSProp,
      SMORMS3,
      Adam~\cite{kingma2015adam},
      AdaMax

@@

  \item {\bf Genetic variants}:
      Conventional Neuro-evolution~\cite{Belew_1990},
      Covariance Matrix Adaptation Evolution Strategy~\cite{Hansen_2001}

  \item {\bf Other}:
    Conditional Gradient Descent,
    Frank-Wolfe algorithm~\cite{Frank_1956},
    Simulated Annealing~\cite{kirkpatrick1983optimization}

@@

using namespace ens;
StandardSGD<>().Optimize(lrf, sgdModel);
Adam().Optimize(lrf, adamModel);
AdaGrad().Optimize(lrf, adagradModel);
SMORMS3().Optimize(lrf, smorms3Model);
SPALeRASGD().Optimize(lrf, spaleraModel);
RMSProp().Optimize(lrf, rmspropModel);
\end{minted}
\caption{Code.}
\end{subfigure}
\begin{subfigure}[b]{0.49\textwidth}
  \centering
  % \includegraphics[width=\textwidth,height=0.45\textwidth]{experiments/learning_curves_crop.png}
  \includegraphics[width=\textwidth,height=0.6\textwidth]{experiments/learning_curves_crop.eps}
  %% CS: to remove the blank space around the plot:
  %% CS: epstool --copy --bbox input.eps output.eps
\caption{Learning curves.}
\end{subfigure}
\caption{\footnotesize
Example usage of six \texttt{\small ensmallen} optimizers to optimize a
linear regression function on the \texttt{\small YearPredictionMSD}
dataset~\cite{ucimlrepository} for 5 epochs of training.  The optimizers can be
tuned for better performance.}
\label{fig:learning_curve}
\vspace*{-1ex}
\end{figure}

@@

We aim to expand the library with further optimization techniques
as the need arises.  Since {\tt ensmallen} is open source,
external contributions to the codebase are welcome.
For more information on the
library, see the website and documentation at
\href{https://www.ensmallen.org}{\tt\small https://www.ensmallen.org}.
The library is already in use for function optimization in the
\texttt{\small mlpack} machine learning toolkit~\cite{mlpack2018}.

% RC: I think it's really important to highlight ensmallen's usage (and
% genesis), although I can't find the right words to concisely and non-awkwardly
% say that we wrote ensmallen as part of mlpack originally.
% 
%% CS: good point, though for our purposes i think it's sufficient
%% CS: to simply state that mlpack uses ensmallen.
%% CS: getting into a tangent on the genesis can negatively distract
%% CS: from the central message. besides, there is no room for a proper
%% CS: explanation.
%% CS:
%% CS: I recommend to avoid interchangeably mixing around the words
%% CS: "library", "toolkit", "package" when referring to ensmallen.
%% CS: it's better to consistently stick to "library", and use
%% CS: the other words to refer to other software, such as mlpack.
%% CS: the point is to avoid potential concept clashes
%% CS: (ie. too much overloading on a word), which can lead
%% CS: to confusion as to what exact software we're referring to.
